---
title: "Homework 2"
author: "Ritika Sibal"
date: "`r Sys.Date()`"
output: 
  prettydoc::html_pretty:
    theme: cayman
    toc: true
    number_sections: true
---
## Peer Commentary
I liked how you labelled your chunks for easy navigation of your file. Your chunks all work well. Your histogram was very aesthetically pleasing. You incorporated lost of different elements that I want to learn how to use (if you don't mind, I would love to use this as a template to making my own plots better). I learned that I don't need to put a range on the x parameter, so thank you for showing me that. Additionally, I noticed that in HW2.5, you placed a parenthesis around the variable holding the simulated calls, which displayed the variable contents. I usually just retype the name but it seems you know a better way. Maybe this isn't that difficult, but I would recommend commenting on your codes when they begin to get long or difficult to keep track of everything. Thanks for showing me that.
Don't forget Titi monkey image!

## Background

Background: Every Saturday, at the same time, a primatologist goes and sits in the forest in the morning and listens for titi monkey calls, counting the number of calls they hear in a 2 hour window from 5am to 7am. Based on previous knowledge, she believes that the mean number calls she will hear in that time is exactly 15. Let X represent the appropriate Poisson random variable of the number of calls heard in each monitoring session.

## What is the probability that she will hear more than 8 calls during any given session?

``` {r HW2.1}
# We know lambda is the "mean number of occurrences of the event in the given interval"
# Thus, our lambda will be 15 in a 2 hour interval
l<-15
x = 8 # 8 calls
ppois(q = x, lambda = l, lower.tail=FALSE)

```

## What is the probability that she will hear no calls in a session?
``` {r HW2.2} 
x<-0 
dpois(x = x, lambda = l)
```

## What is the probability that she will hear exactly 3 calls in a session?
``` {r HW2.3} 
x<-3 
dpois(x = x, lambda = l)
```

## Plot the relevant Poisson mass function over the values in range 0 ≤ x ≤ 30.
``` {r HW2.4} 
x<-0:30
probset <- dpois(x = x, lambda = l)
barplot(probset, names.arg = x, space = 0, xlab = "x", ylab = "Pr(X = x)", main = "Probability Mass Function")
```

## Simulate 104 results from this distribution (i.e., 2 years of Saturday monitoring sessions).
``` {r HW2.5} 
n = 104
(results<-rpois(n, l))
```

## Plot the simulated results using hist() and use xlim() to set the horizontal limits to be from 0 to 30. How does your histogram compare to the shape of the probability mass function you plotted above


As seen in the graphical output, the histogram created from the randomly simulated results does generally, but not perfectly, follow the Poisson Distribution generated with lamba=15. This makes sense as the randomness of the rpois() function will also lead to some randomness in the results, making our histogram/results not perfectly poisson-ly distributed.

``` {r HW2.6} 
x<-0:30
probset <- dpois(x = x, lambda = l)

#supress histogram plot first
p1<-hist(results, breaks=30, plot=FALSE)
plot(p1, xlim=c(0,30), col='blue', xlab='Number of calls (in 2hr interval)', ylab='Frequency of calls', main = " Titi Monkey calls heard in n=104 trials")
lines(probset*n, col='red')

# Used this to scale legend: https://www.geeksforgeeks.org/change-legend-size-in-base-r-plot/
legend("topleft", cex=0.9, c("Simulated Calls", "Poisson Distributed Calls"), fill=c("blue", "red"))
```
