---
title: "Homework 2"
author: "Ritika Sibal"
date: "`r Sys.Date()`"
output: 
  prettydoc::html_pretty:
    theme: cayman
    toc: true
    number_sections: true
---
<center>
<iframe width="560" height="315" src="https://www.youtube.com/embed/sTtPAu3vNzQ?si=4uQ2aTxkh1PrOLRI" data-external= "1" > </iframe>

<br> *Got information about embedded video from: https://stackoverflow.com/questions/38517236/youtube-video-in-r-markdown*
</center>

## Background

Background: Every Saturday, at the same time, a primatologist goes and sits in the forest in the morning and listens for titi monkey calls, counting the number of calls they hear in a 2 hour window from 5am to 7am. Based on previous knowledge, she believes that the mean number calls she will hear in that time is exactly 15. Let X represent the appropriate Poisson random variable of the number of calls heard in each monitoring session.

## What is the probability that she will hear more than 8 calls during any given session?

``` {r HW2.1}
# We know lambda is the "mean number of occurrences of the event in the given interval"
# Thus, our lambda will be 15 in a 2 hour interval
l<-15
x = 9 # 9 calls since the question asks for MORE than 8
# lower.tail=FALSE gives us everything >9
ppois(q = x, lambda = l, lower.tail=FALSE)

```

## What is the probability that she will hear no calls in a session?
``` {r HW2.2} 
x<-0 # 2 calls
dpois(x = x, lambda = l)
```

## What is the probability that she will hear exactly 3 calls in a session?
``` {r HW2.3} 
x<-3 # 3 calls
dpois(x = x, lambda = l)
```

## Plot the relevant Poisson mass function over the values in range 0 ≤ x ≤ 30.
``` {r HW2.4} 
x<-0:30 # Range 0 ≤ x ≤ 30
probset <- dpois(x = x, lambda = l)
barplot(probset, names.arg = x, space = 0, xlab = "x", ylab = "Pr(X = x)", main = "Probability Mass Function")
```

## Simulate 104 results from this distribution (i.e., 2 years of Saturday monitoring sessions).
``` {r HW2.5} 
n = 104
(results<-rpois(n, l)) # rpois simulates random data, adding () will output data onto console in one command
```

## Plot the simulated results using hist() and use xlim() to set the horizontal limits to be from 0 to 30. How does your histogram compare to the shape of the probability mass function you plotted above


As seen in the graphical output, the histogram created from the randomly simulated results does generally, but not perfectly, follow the Poisson Distribution generated with lamba=15. This makes sense as the randomness of the rpois() function will also lead to some randomness in the results, making our histogram/results not perfectly poisson-ly distributed.

``` {r HW2.6} 
x<-0:30
probset <- dpois(x = x, lambda = l)

# histogram plot first
p1<-hist(results, breaks=30, plot=FALSE)
plot(p1, xlim=c(0,30), col='blue', xlab='Number of calls (in 2hr interval)', ylab='Frequency of calls', main = " Titi Monkey calls heard in n=104 trials")
# Add a line to the histogram plot showing the true poisson distribution, I did this by just multiplying the Poisson distribution created in the last step (probset) by n=104.
lines(probset*n, col='red')

# Used this to scale legend: https://www.geeksforgeeks.org/change-legend-size-in-base-r-plot/
legend("topleft", cex=0.9, c("Simulated Calls", "Poisson Distributed Calls"), fill=c("blue", "red"))
```

## Reflection 
**When I was coding:**

*3 things were difficult: *
<br> 1) I still have some trouble in the development phase, I am tending to test everything in the console forgetting that I can run chunks of data!
<br> 2) Graphing was hard this time! I wanted to add a line to my histogram chart and it was difficult to figure out how to do in base R--I ultimately realized that I was not bin-ing my data correctly 
<br> 3) Embedding the video was interesting! I finally realized what the embed link on Youtube is for. 

*3 ways your peers commentary helped you:*
<br> 1) I had missed that the first question asked for MORE than 8, not 8 and more! 
<br> 2) I had also forgotten to add the titi monkey video/photo
<br> 3) My partner suggesting adding more comments in my code and upon reflection I agree! I think I can do a better job of commenting

**When I was Peer Commentating:** 

*2 things you liked in your peers code:*
<br> 1) My peer commented their code very well, from a reader perspective it was very easy to understand
<br> 2) My peer plotted their answers for more questions than we were required to and I felt it really helped my visualise the data!

*1 thing that could use improvement:*
<br> 1) My peer partner gave the explanation for how the simulated histogram varied from the actual Poisson distribution based on what compiled on her computer but I encouraged her to give a more general answer as each complication will result in different values since we used the rpois command!